Hybrid oddball - SSVEP BCI

### 2013-06-18 draftHybridPaper/draftHybridBCI.tex
it's been a while

        \subsubsection{Experimental protocol}
        \label{sec:2.2.1Protocol}

@@

        \subsubsection{Data Analysis: \acs{ERP} responses}
        \label{sec:2.2.2AnalysisErpShape}

@@

        \subsubsection{Data Analysis: \acs{ERP} classification}
        \label{sec:2.2.3AnalysisErpClassification}

        % studying classification accuracy: no epoch rejection
        We are also interested in studying the effect of the flickering stimulus on the target \ac{ERP} detection accuracy.
        As the accuracy of an oddball \ac{BCI} is known to depend on the number of repetitions of flashing sequences used to average the \acp{ERP}; the classification accuracy was measured on \acp{ERP} averaged over the $n$~first repetitions of the flashing sequence with $n$~going from 1~to~10.
        This was done so as to mimic a real use of the system (where the stimulation sequence would stop after $n$~repetitions) and so that the accuracies are always measured on the same number of detection attempts.

@@

        \subsubsection{Experimental protocol}
        \label{sec:2.3.1Protocol}

        % exp description
        The experimental run was the same as described in \autoref{sec:2.2.1Protocol}.
        Two experimental parameters were manipulated, the first one was the stimulation frequency; the same frequencies as for the first experiment were used (\SIlist[list-units = single]{8.57;10;12;15}{\Hz}).
        The second experimental parameter was the presence or not of the oddball stimulation sequence.
        When the oddball stimulation was displayed, the participants were instructed to count the number of flashes of the target icon, while when no oddball stimulation was displayed, their task was simply to focus on their target icon.

        \subsubsection{Data Analysis}
        \label{sec:2.3.2Analysis}

@@

        \subsubsection{Experimental protocol}
        \label{sec:2.4.1Protocol}

        \subsubsection{Data Analysis}
        \label{sec:2.4.2Analysis}

>>>>

    \subsection{Experimental protocol}
    \label{sec:2.2Protocol}

        \subsubsection{Experiment 1: studying the oddball \acsp{ERP}}
        \label{sec:2.2.1ProtocolOddball}

@@

        \subsubsection{Experiment 2: studying the \acs{SSVEP} responses}
        \label{sec:2.2.2ProtocolSSVEP}

        % exp description
        The experimental run was the same as described in \autoref{sec:2.2.1ProtocolOddball}.
        Two experimental parameters were manipulated, the first one was the stimulation frequency; the same frequencies as for the first experiment were used (\SIlist[list-units = single]{8.57;10;12;15}{\Hz}).
        The second experimental parameter was the presence or not of the oddball stimulation sequence.
        When the oddball stimulation was displayed, the participants were instructed to count the number of flashes of the target icon, while when no oddball stimulation was displayed, their task was simply to focus on their target icon.

        \subsubsection{Experiment 3: hybrid classification}
        \label{sec:2.2.3ProtocolHybrid}

        After studying individually oddball \acp{ERP} and \ac{SSVEP} responses, we aim here at studying the possibility to detect both responses

    \subsection{Data Analysis}
    \label{sec:2.3DataAnalysis}

        \subsubsection{Experiment 1: ERPs classification}
        \label{sec:2.3.1AnalysisExp1}

@@

%%%%%%%%        \subsubsection{Data Analysis: \acs{ERP} classification}
%%%%%%%%        \label{sec:2.2.3AnalysisErpClassification}

        % studying classification accuracy: no epoch rejection
        We are interested in studying the effect of the flickering stimulus on the target \ac{ERP} detection accuracy.
        As the accuracy of an oddball \ac{BCI} is known to depend on the number of repetitions of flashing sequences used to average the \acp{ERP}; the classification accuracy was measured on \acp{ERP} averaged over the $n$~first repetitions of the flashing sequence with $n$~going from 1~to~10.
        This was done so as to mimic a real use of the system (where the stimulation sequence would stop after $n$~repetitions) and so that the accuracies are always measured on the same number of detection attempts.

@@

        \subsubsection{Experiment 2: SSVEP response analysis}
        \label{sec:2.3.2AnalysisExp2}

@@

        \subsubsection{Experiment 3}
        \label{sec:2.3.3AnalysisExp3}
